---
title: "Using Valve with Docker"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Valve is intended to make plumber APIs more effective in a production setting. It is recommended to deploy plumber APIs to production in a Docker container (or use [Posit Connect](https://posit.co/products/enterprise/connect/) if you have company budget and more use cases than a single API).

At the end is an example `Dockerfile` that can act as a reference for you. If you have an existing Dockerfile that you use to deploy a plumber API, all you need to do to use Valve is to 1) install Rust, 2) install Valve, and 3) change your `ENTRYPOINT`. Below are the key additional and changes you would have to make.

```docker
# Install Rust toolchain & add to the path
RUN apt-get install -y -q build-essential curl
RUN curl https://sh.rustup.rs -sSf | sh -s -- -y
ENV PATH="/root/.cargo/bin:${PATH}"

# Install Valve binary from Github
RUN cargo install valve-rs --no-default-features

# Start Valve app
ENTRYPOINT valve -f /api/plumber.R -h 0.0.0.0 -p 8000 --workers 10 --n-max 10 --check-unused 10 --max-age 300
```

The first 3 commands install the appropriate system requirement to install Rust, install Rust, then adds `cargo` to the path. Afterwards, the valve binary is installed from `crates.io`. Lastly, an `ENTRYPOINT` is defined to fun your plumber API. 

The `ENTRYPOINT` is where you have control over how Valve will scale. Most importantly, the `-f` flag should point to a `plumber.R` script—whereever that might be in your Dockerfile. The host _must_ be `0.0.0.0` for a Docker container. You can configure the additional arguments as you need. See the README for more on how these arguments work. 

## Example `Dockerfile`

```{r, echo = FALSE}
cat(readLines(system.file("docker/Dockerfile", package = "valve")), sep = "\n")
```
The above Dockerfile is included in `{valve}` and can be found via `system.file("docker/Dockerfile", package = "valve")`. It was build with the included plumber API `system.file("docker/plumber.R", package = "valve")`.

To replciate, copy the files into a directory of your choosing. Ensure Docker desktop is open. Then build the container with `docker build -t valve:latest .`. Then you can run the container with: 

```shell
docker run -p 8000:8000 valve:latest
```
